---
title: "Movie Recommendation Case Statement"
author: "Me"
date: "`r Sys.Date()`"
output: html_document
---

```{r message=FALSE}
library(arules)
library(shiny)
```


## Developing recommendations (template for app)

Let's develop a set of recommendations for the set of liked movies in the last chunk.  Since debugging a Shiny app is hard, it's best to anticipate what inputs the app will have, then work through an example by hand of how the app should work.  A powerful way to do this is the define a list object named `input` (since that's what Shiny uses to references what the user selected) and to write code in terms of its elements

```{r}
load("MOVIERECSpring2022.RData")
```

In shiny you'll be dealing with user inputs via `input$input_id`.  It can be helpful when planning code to fake a list of inputs.

Example:

```{r}
# Create an empty container
input <- list()

# Add in options
input$selected_options <- c("Space Jam", "Up")
input$my_checkbox <- TRUE

# Extract the same as in shiny
input$selected_options
input$my_checkbox
```

Below is an example we can use to build our rec engine.

```{r}
# INPUTS START -------------------------------------------
input <- list()

# Simulate a selectInput for movies

# Check 1 from assignment page
input$selected_movies <- c(
  "Shawshank Redemption, The (1994)","Godfather, The (1972)",
  "Dark Knight, The (2008)", "Pulp Fiction (1994)",
  "Schindler's List (1993)","12 Angry Men (1957)",
  "Inception (2010)","Fight Club (1999)"
)

# Simulate a numericInput/sliderInput for number of recs
input$number_of_recs <- 10

# Simulate a numericInput/sliderInput for min rec confidence
input$min_confidence <- 0.25

# Simulate a numericInput/sliderInput for max popularity allowed
input$max_popularity <- 5

input$sorting <- 2
# INPUTS END -------------------------------------------

# REC CODE START   ----------------------------------------
RECS <- NULL
if (isTruthy(input$selected_movies)) {
  # Rule out too popular movies early on
  too_popular <- POPULARITY$title[which(100 * POPULARITY$percentSeen > input$max_popularity)]
  
  # Keep popular movies that the user input
  too_popular <- setdiff(too_popular, input$selected_movies)

  min_support <- 4
  max_time <- 0

  RULES <- apriori(
    TRANS,
    parameter = list(
      supp = min_support / length(TRANS),
      conf = input$min_confidence,
      minlen = 2,
      maxtime = max_time
    ),
    appearance = list(
      none = too_popular,
      lhs = input$selected_movies,
      default = "rhs"
    ),
    control = list(
      verbose = FALSE
    )
  )

  if (length(RULES) > 0) {
    RULES <- RULES[!is.redundant(RULES)]
    RULES <- RULES[is.significant(RULES, TRANS)]

    RULESDF <- DATAFRAME(RULES, itemSep = " + ", setStart = "", setEnd = "")
    names(RULESDF)[1:2] <- c("BasedOn", "title")

    # Remove recs that the user gave as input
    RULESDF <- RULESDF[!(RULESDF$title %in% input$selected_movies), ]
    if (nrow(RULESDF) > 0) {
      RECS <- aggregate(confidence ~ title, data = RULESDF, FUN = max)

      RECS <- merge(RECS, POPULARITY, by = "title")

      RECS$item_id <- NULL
      RECS$countSeen <- NULL
      RECS$Year <- NULL
      names(RECS) <- c("Movie", "Confidence", "PercentSeen", "imdbRating")

      # Order the recommendations by confidence
      RECS <- RECS[order(RECS$Confidence, decreasing = TRUE), ]
      #RECS <- RECS[order(RECS[,input$sorting] , decreasing = TRUE), ]
      RECS <- head(RECS, input$number_of_recs)

      # Take out confusing row names
      row.names(RECS) <- NULL
      
      RECS$Confidence <- round(RECS$Confidence * 100, 2)
      RECS$PercentSeen <- round(RECS$PercentSeen * 100, 2)
    }
  }
}

if (is.null(RECS)) {
  RECS <- data.frame(
    Error = "No recommendations with these parameters.  Add more movies, decrease confidence, or increase popularity!"
  )
}

order_by <- RECS[,input$sorting]
RECS <- RECS[order(RECS$Confidence, decreasing = TRUE), ]

RECS
# REC CODE END     ----------------------------------------
```

```{r}
RECS <- RECS[order(RECS[,2] , decreasing = TRUE), ]
RECS
```


## Goals of the Assignment 

Your job is to write a Shiny App that serves as a recommendation engine for "hidden games", obscure movies that only a tiny percentage of user of Movielens have rated.

Shiny App requirements:

* A `selectInput` to allow users to select multiple movies to base a recommendation on
* A `sliderInput` or `numericInput` for user to input number of recommendations (up to 100)
* A `sliderInput` or `numericInput` for user to input number of minimum confidence
* A `sliderInput` or `numericInput` where the user inputs the maximum "popularity" of a movie
  * Popularity as percentage of users in data that have rated the movie at all
  * Petrie recommends having these popularities as numbers 0-30 to represent the percentages.
* Give user ability to sort columns
  * At least choice between sorting by confidence and sorting by title alphabetically
* A "button" to for users to click to update recommendations
* A table of recommendations
  * with 4 columns
    * Movie title
    * Confidence (as a number between 0-100; rounded to 1 digit after the decimal)
    * PercentSeen (as a number between 0-100; rounded to 2 digits after the decimal)
    * imdbRating
  * By default sort the table by Confidence
